---
title: "ALY6040 Week 1 Assignment Hang"
output:
  html_document:
    df_print: paged
  word_document: default
---
This is about the single assignment on Sales Data on IceC
it has all the code from before so I don't have to sample them from scratch

---
##Install the neccessary libraries
```{r}

#1. Print the Name of the person and the project
print("ALY6015 Week 3:Hang Wu")

#Install important packages that will be imported in stage #2
# install.packages("Hmisc")
# install.packages("car")
# install.packages("corrplot")
# install.packages("function")
# install.packages("data")
# #use R 3.6.3 to use the FSA and FSAdata packages
# install.packages("FSA") #select no to compilation, this will make sure the FSA package is imported. 
# install.packages("moments")
# #install.packages("rowr")
# # install.packages("ggpubr")
# install.packages("ggplot2")
# install.packages('psych')
# install.packages("formattable")
# install.packages('knitr', dependencies = TRUE)
# install.packages('FSelector')
# install.packages("corrr") 
# install.packages("dplyr")  
# install.packages("Hmisc")
# install.packages('mlbench')
# install.packages(c("cluster.datasets"), dependencies = TRUE)
# install.packages('caTools')
# install.packages("plotrix")      # Install plotrix package
# install.packages("dlookr")
#install.packages('broom')
#install.packages('olsrr')
```
```{r}

```


##1、 Load the file
```{r}
#clean all data from the workspace
rm(list = ls())
#close all figures in R Studio
#dev.off(dev.list()["RStudioGD"])

#2.Import libraries including: FSA, FSAdata, magrittr,  dplyr, plotrix, plot2, and moments
library(dplyr)
library(ggplot2)
library(corrplot)
library(RColorBrewer)
library(car)
library(MASS)
library(corrplot)
library(FSAdata)
library(FSA)
library(magrittr)
```


```{r}
library(dplyr)
#library(tydir)
library(tidyverse)
library(plyr)
```


```{r}
library(moments)
# load e1081, for kurtosis
#library(e1081) 
library(grid) #used for watermark
#library(rowr) 
library(psych)
library(formattable)
library(knitr)
library(FSelector)
library(moments)
library(corrr)
library("Hmisc") #use rcorr
library(cluster.datasets)
library("plotrix")               # Load plotrix
library(dlookr)
library(forcats)
library('broom')
library('olsrr')

```


```{r}
#2. IMPORT the data.csv data in R,
getwd()
setwd("/Users/hangwu/Desktop/Northeastern/6040/Assignment 2")

#Data Read and Data Cleaning
IceC <- read.delim("KickstarterData_Facts.csv", sep=",") #since bank data is ; delimited, read.delim is used rather than read.csv
headtail(IceC)
class(IceC)
str(IceC)
describe(IceC)
#IceC = na.omit(IceC)
df = IceC
#res <- gain.ratio(g~., df)

df[is.na(df[1:10000,])==TRUE]
df[is.null(df)]
listname<-df
!is.null(listname) & class(listname) != "NULL" & class(listname) != "logical" & length(listname) != 0

sum(df$Preferred.Color.of.Device=="") # Sum of empy cell of myvar
sum(df$How.many.desserts.do.you.eat.a.week=="") # Sum of empy cell of myvars
sum(df$Deposit.Amount=="") # Sum of empy cell of myvar
which(df$Deposit.Amount=="", arr.ind=TRUE) # Specify which are empty
##which row and column are NA
which(is.na(df)==TRUE,arr.ind=TRUE)
##144 fields are NA

```


```{r}
# #replace the NULL's with 0
# df[is.null(df)] <- 0
# #replace the NA with 0
# df[is.na(df)] <- 0
# 

# #takes backup of df
# df.backup <- df
# 
# is.null(df$Donate.ID)
```

##Table of Summary and the Chart
```{r}
```



##Table of Summary
```{r}
#table
formattable(describe(IceC), list(
  kurtosis = color_tile("white", "orange"),
  skew = color_tile("white", "red"),
  se = color_tile("white", "blue"),
  range = formatter("span", style = x ~ ifelse(x == "A",
                                               style(color = "green", font.weight = "bold"), NA)),
  #area(col = c(sd, se),row=TRUE) ~ normalize_bar("pink", 0.2),
  def = formatter("span",
                          style = x ~ style(color = ifelse(rank(-x) <= 3, "green", "gray")),
                          x ~ sprintf("%.2f (rank: %02d)", x, rank(-x))),
  abc = formatter("span",
                         style = x ~ style(color = ifelse(x, "green", "red")),
                         x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No")))
))
df.des = describe(IceC)
df.des.sp <- as.data.frame(unlist(df.des["Deposit.Amount",]))

ggplot(df.des, aes(x = factor(df.des$variable), y = df.des$kurtosis,group=df.des$kurtosis, 
                      fill = df.des$variable,label = df.des$kurtosis)) +

  geom_col(position = "fill") +
  #geom_label(aes(label = percent(percent)), position = "fill", color = "white", vjust = 1, show.legend = FALSE,size=3) +
   geom_text(check_overlap = TRUE,aes(label = df.des$kurtosis), position = "fill", color = "black", vjust = 1, show.legend = FALSE,size=3)+
     xlab('Shot Outcome')+
  ylab('Percentage(%) ')+
   # scale_x_discrete(limits=c(1,2,3,4))+
  #scale_y_continuous(labels = percent,limits=c(0,0.4))+
  #theme(plot.margin = unit(c(1,2,2,1), "cm"))+
  theme(text=element_text(size=10, vjust=3))+
  theme(strip.text = element_text(size=5, vjust=1))
#+
 #facet_grid(~plot_data$bodypart)
ggsave('plotKurtosis.png')
```

##Using Box Chart
```{r}
p<-ggplot(df) +
  aes(x = "", y = Deposit.Amount) +
  geom_boxplot(fill = "#0c4c8a") +
  theme_minimal() +ylim(1,300)
p + ggtitle("Plot 1a. Sale Price Box Chart") +
  xlab("IceC") + ylab("Sale Price($)")


```

##Histogram/Density Diagram
```{r}
#Using Histogram
# Add mean line
p+ geom_vline(aes(xintercept=mean(df$Deposit.Amount)),
              color="blue", linetype="dashed", size=1)
# Histogram with density plot
p.p<-ggplot(df, aes(x=df$Deposit.Amount)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666") +xlim(80,300)

p.p + ggtitle("Density Histogram for Donation Amount") +
  xlab("Donation($)") + ylab("Density")

ggsave("densityplot.png")

#histogram(df$Deposit.Amount)
df$Deposit.Amount
##which ones are deposited
count(which(df$Deposit.Amount>150,arr.ind=TRUE)) ##2237 results
count(which(df$Deposit.Amount>300,arr.ind=TRUE)) ##872 results
count(which(df$Deposit.Amount>1000,arr.ind=TRUE)) ##1 results
df[df$Deposit.Amount>1000,]


```
##Data Cleaning: change null/NA to the median of respective field.
##haven't eliminated the outliers because they aren't outliers, it's just not many people who donate a lot
##if anything, we should learn more about the person who donated more, and attract people like him/her
```{r}
df$Deposit.Amount <- df$Deposit.Amount %>% replace(.=="NULL", median(df$Deposit.Amount)) # replace with the median because it's heavily skewed
df$Ice.Cream.Products.Consumed.Per.Week <- df$Ice.Cream.Products.Consumed.Per.Week %>% replace(.=="NULL", median(df$Ice.Cream.Products.Consumed.Per.Week)) # replace with the median because it's heavily skewed


df$Deposit.Amount <- df$Deposit.Amount %>% replace(.==NA, median(df$Deposit.Amount)) # replace with the median because it's heavily skewed
df$Ice.Cream.Products.Consumed.Per.Week <- df$Ice.Cream.Products.Consumed.Per.Week %>% replace(.==NA, median(df$Ice.Cream.Products.Consumed.Per.Week)) # replace with the median because it's heavily skewed

df$Deposit.Amount[is.na(df$Deposit.Amount)]<- mean(na.omit(df$Deposit.Amount))
df$Ice.Cream.Products.Consumed.Per.Week[is.na(df$Ice.Cream.Products.Consumed.Per.Week)]<- mean(na.omit(df$Ice.Cream.Products.Consumed.Per.Week))


```


##Split df into catergorical and numerical, and build correlation for the numeric df.Num
##using chi-sqr independence test for categorical ones, or ANNOVA
```{r}
#convert all character columns to factor
df <- as.data.frame(unclass(df), stringsAsFactors = TRUE) 
df.Num <- select_if(df, is.numeric) #select only numeric column
df.Ord <- select_if(df, is.factor) #select only ordinal column
```

##seems the replacement doens't work, use na.omit
```{r}

#df.Num<-na.omit(df.Num)
#is.na(df.Num)
```

##Scatter Matrix for linearity, of course with GLM it's gonna be much more appearant
```{r}
#
pairs(df.Num)
```
##Correlation Matrix Attempt 1
```{r}
correlation <- cor(df.Num)

#png( file="P2correlationPlot.png", type = "cairo")
corrplot(correlation, method="number",is.corr = FALSE, 
         main ="Plot 2a: Correlation Matrix of All Numeric Attributes",
         mar = c(1, 2, 2, 1),
         pch=4,
         cl.ratio=0.4,
         tl.cex = 0.5
         
         )#tl changes the label of the legendß
    
#dev.off()

```
##p-value matrix of the Correlation
##Create P-value Matrix for correlation
```{r}
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
```

##call the custome function
```{r}

p.mat<-cor.mtest(select_if(df,is.numeric))
```

##correlation with p-value matrix

```{r}
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor(df.Num), method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
          main ="Plot 2b: Correlation Matrix of All Numeric Attributes(Style 2)",
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )


col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
##corrplot(cov2cor(cov(df.Num)), method="color",is.corr = T, 
corrplot(cov2cor(cov(df.Num)), method="color",is.corr = T, 
         col=col(200),  
         type="upper", order="hclust",
         main ="Plot 2b: Correlation Matrix of All Numeric Attributes(style 2)",
         mar = c(1, 2, 2, 1),
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         p.mat = p.mat, 
         sig.level = 0.05, 
         insig = "blank",
          # hide correlation coefficient on the principal diagonal
         diag=FALSE,
         pch=4,
         cl.ratio=0.4,
         tl.cex = 0.5,
         number.cex=0.25)#tl changes the label of the legend

library(Hmisc)
write.csv(as.data.frame(rcorr(as.matrix(df.Num),type=c("pearson","spearman"))),'DfcorrelationmatrixRR.csv') #record ordered correlation
write.csv(as.data.frame(p.mat),'DfcorrelationmatrixPP.csv') #record ordered correlation


```
##chi square p-value matrix for independence between every column
```{r}
##chi square matrix that record all p values, such that using the p valeus to identify every related columns
chisqmatrix <- function(x) {
  names = colnames(x);  num = length(names)
  m = matrix(nrow=num,ncol=num,dimnames=list(names,names))
  for (i in 1:(num-1)) {
for (j in (i+1):num) {
    #if categoricaal, use xta,else chisq test
    if(is.numeric(x[,i] | is.numeric(x[,j]))){
      m[i,j] = chisq.test(x[,i],x[,j],)$p.value
      #n[i,j]=  chisq.test(x[,i],x[,j],)$residuals
    }else{
      
       m[i,j] = chisq.test(xtabs(~ x[,i] + x[,j], data = df,addNA = TRUE),)$p.value
    }
      
    }
  }
  return (m)
}
```
```{r}
mat = chisqmatrix(df)
write.csv(as.data.frame(mat),'ChisqPValueMatrixFull.csv') #record p-value

```


```{r}
write.csv(formattable(summary(df.Ord)),"Categorical_data_summary.csv")

```

##Rank of household income vs Deposit
```{r}
lvls<-seq(from=1,to=10,by=1)

chisq <- chisq.test(df$ Deposit.Amount,lvls[df$Household.Income])

mySample <- mySample %>% mutate(SalePrice_ntile = ntile(mySample$SalePrice, 5))


```

##how many eat icecream if they eat desert
```{r}
count(df[df$How.many.desserts.do.you.eat.a.week,])
shapiro.test(df.Num$Deposit.Amount[1:5000])
df$Donate.Date.Rank <- lvls[df$Donate.Date]
df$Household.Income.Rank<-lvls[df$Household.Income]
summary(df[df$Do.you.own.a.Keurig=="no",])

```


```{r}
summary(df)
#df$Donate.Date
```
```{r}
df.Num <- select_if(df, is.numeric) #select only numeric column
df.Ord <- select_if(df, is.factor) #select only ordinal column

p.mat<-cor.mtest(select_if(df,is.numeric))
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
##corrplot(cov2cor(cov(df.Num)), method="color",is.corr = T, 
corrplot(cov2cor(cov(df.Num)), method="color",is.corr = T, 
         col=col(200),  
         type="upper", order="hclust",
         main ="Correlation Matrix of All Numeric and Ordinal",
         mar = c(1, 2, 2, 1),
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         p.mat = p.mat, 
         sig.level = 0.05, 
         insig = "blank",
          # hide correlation coefficient on the principal diagonal
         diag=FALSE,
         pch=4,
         cl.ratio=0.4,
         tl.cex = 0.5,
         number.cex=0.25)#tl changes the label of the legend

```
```{r}
df$Do.you.own.a.Keurig
df$Donated.To.Kick.Starter.Before
```

```{r}
if(!require('rpart.plot')) {
    install.packages('rpart.plot')
    library('rpart.plot')
}

old.par <- par(mfrow=c(2,2))            # put 4 figures on one page


#---------------------------------------------------------------------------

binary.model <- rpart(Purchased ~ ., data = df, cp = .02)
                                        # cp = .02 for small demo tree

rpart.plot(binary.model,
           main = "People Purchased the Machine\n(binary response)")

rpart.plot(binary.model, type = 3, clip.right.labs = FALSE,
           branch = .4,
           box.palette = "Grays",       # override default GnBu palette
           main = "type = 3, clip.right.labs = FALSE, ...\n")

#---------------------------------------------------------------------------

anova.model <- rpart(Deposit.Amount ~ ., data = df)

rpart.plot(anova.model,
           shadow.col = "gray",         # add shadows just for kicks
           main = "miles per gallon\n(continuous response)\n")

#---------------------------------------------------------------------------

multi.class.model <- rpart(Gender ~ ., data = df)

rpart.plot(multi.class.model,
           main = "vehicle reliability\n(multi class response)")

par(old.par)

```
```{r}
####### Chi Square Indep

chisq <- chisq.test(df$Purchased,df$Preferred.Color.of.Device)
chisq$observed
round(chisq$expected,2)
round(chisq$residuals, 3)
round(chisq$stdres,3)


# Chi Square Testing:  Whether Gross Revenue is dependent on Content Rating
myChisq <- xtabs(~ df$Purchased + df$Preferred.Color.of.Device, data = df)
#myChisq  #for printing the cross tabulation

chisq.test(myChisq) # running chi-square test

# here we write one single line of command to produce result xtabs is specified inside chisq.test()
chisq.test(xtabs(~ df$Purchased + as.factor(df$Preferred.Color.of.Device), data = df)) 

# Initialize file path
file_path= "Correlation matrix.png"
png(height=1800, width=1800, file=file_path, type = "cairo")

corrplot(chisq$residuals, is.cor = FALSE)

# Then
dev.off()
```


```{r}
########### ANOVA
# 
# str(df$Exterior.1st)
# y<-df$SalePrice
# A<-df$Exterior.1st
# B<-df$Neighborhood
# class(B)
# 
# X = count(B)[order(count(B)$freq),]
# write.csv(as.data.frame(X),'Frequency of Neighborhood.csv') 
# Y = count(A)[order(count(A)$freq),]
# write.csv(as.data.frame(Y),'Frequency of Exterior.csv') 
# 
# ###drop categories with low freq
# B[levels(B)==c('Other','AsphShn','CBlock','Stone')]=0
# B <- B[-c('Other','AsphShn','CBlock','Stone')] #drop levels
# new_B <- subset(B, levels(B)!=c('Other','AsphShn','CBlock','Stone'))
# 
# #drop unused factor levels
# B <- droplevels(B)
# B<-new_B
# str(B)
# 
# A[levels(A) == c('ImStucc','Stone','AsphShn','CBlock','BrkComm')]=0
# levels(A)
# new_A1<-A[-c(8,12,2,5,2)]
# length(new_A1) #2388
# length(A) #2392
# new_A <- subset(A, levels(A)!=c('ImStucc','Stone','AsphShn','CBlock','BrkComm'))
# length(new_A)#2243
# A <- droplevels(A)
# A<-new_A
# 
# ##freqeuncy plot to see the category
# p.p<-ggplot(data.frame(X), aes(x=X$x,y=X$freq)) + 
#   geom_bar(stat="identity")
# #colour="black", fill="white")+
# #geom_density(alpha=.2, fill="#FF6666") 
# p.p + ggtitle("Plot Tri 3. Expected Frequency") +
#   xlab("Cost Benefit Ratio") + ylab("Density")
# ggsave("Plot5Alpha1.png")
# 
# 
# # Two Way Factorial Design
# fit <- aov(y ~ A + B + A:B, data=df)
# fit <- aov(y ~ A*B, data=df) # same thing
# 
# png(file=file_path, type = "cairo")
# layout(matrix(c(1,2,3,4),2,2)) # optional layout
# # Initialize file path
# file_path= "Diagnostic Plot.png"
# 
# plot(fit) # diagnostic plots
# dev.off()
#############################
```

##Feature Selection: Feature Improtance
```{r}
# ensure results are repeatable
set.seed(7)
# load the library
#install.packages('mlbench')
#install.packages('caret')
library(mlbench)
library(caret)
# load the dataset
data(PimaIndiansDiabetes)
# prepare training scheme
control <- trainControl(method="repeatedcv", number=10, repeats=3)
# train the model
#model <- train(diabetes~., data=PimaIndiansDiabetes, method="lvq", preProcess="scale", trControl=control)
model <- train(as.factor(Purchased)~., data=df[1:1000,], method="lvq", preProcess="scale", trControl=control)
# estimate variable importance
importance <- varImp(model, scale=FALSE)
# summarize importance
print(importance)
# plot importance
plot(importance)

```
#Feature Selection: RFE(Rercursive Feature Elimination)
```{r}
# define the control using a random forest selection function
control <- rfeControl(functions=rfFuncs, method="cv", number=10)
# run the RFE algorithm
results <- rfe(df[1:1000,1:11], df[1:1000,12], sizes=c(1:11), rfeControl=control)
# summarize the results
print(results)
# list the chosen features
predictors(results)
# plot the results
plot(results, type=c("g", "o"))

```
##Feature Selection: Correlation Method
```{r}

data(PimaIndiansDiabetes)
# calculate correlation matrix
correlationMatrix <- cor(df.Num[,1:4])
# summarize the correlation matrix
print(correlationMatrix)
# find attributes that are highly corrected (ideally >0.75)
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.5)
# print indexes of highly correlated attributes
print(highlyCorrelated)
```

##GLM Modelling
```{r}
##GLM:Binomial

#getwd()
#setwd("/Users/hangwu/Desktop/Northeastern/6015/Final Assignment/GLM")
options(warn=-1)

#hist(dfC.merge.2$is.team.winning)
#fitting the logistic model using glm() function:  also activated the trace option
 fit1.isPurchased<- glm(as.factor(Purchased) ~ Gender+df$How.many.desserts.do.you.eat.a.week+df$Preferred.Color.of.Device+df$Ice.Cream.Products.Consumed.Per.Week ,data=df, family=binomial (link="logit"), control=glm.control(trace=FALSE))

##this model takes way too long to finish


saveRDS(fit1.isPurchased, "fit1.isPurchased.rds")

#
# #getting the regression output
 s.is.win<-summary(fit1.isPurchased)
 or.is.win<-S(fit1.isPurchased)

or.is.win

write.csv(s.is.win$coefficients,"Fit1BiGoalProbabilityPredictionCoe.csv")
write.csv(or.is.win$exponentiated,"Fit1BiGoalProbabilityPredictionEXP.csv")
```


```{r}
#event level
 fit1.is.win.bi.log<- glm(is.team.winning ~ is.miss*+is.assist+is.miss+pr.match.card+goal.in.15*pr.match.card+is.foul++pr.misses,data=dfC.merge.2, family=binomial (link="logit"), control=glm.control(trace=FALSE))



saveRDS(fit1.is.win.bi.log, "fit2.is.win.bi.log.rds")

#
```


